### 2016-11-29 Chapters/introduction.tex
Uncomplete version of intro sent to Hidde/Hans, add rem_intro.md that describe what is missing.

What makes mathematical modeling so useful in microbial growth studies?
Microbial physiology comes out from the interplay of thousands of chemical reactions that are not necessarily relevant in any given situation.
They usually occur on a short time scale as compared with the organism life span.
They nevertheless have been (and still are) selected by evolutionary processes that occur on long time scales.
These physical limitations strongly impede a full empirical study of growth processes, making sometimes hard to test the most simple verbal hypothesis.

Since they are designed to abstract away complexity, mathematical models are great tools to deal with such limitations.
The overwhelming number of variables and time scales can be dealt with by choosing the correct framework.
When working on a model, growth is abstracted into a world of clearly stated rules, where logical reasoning can be applied~\cite{servedio_not_2014}.
Predictions can be made, "unpacked" into our real world, and confronted with experimental testing.
In that sense, modeling is at the core of the scientific method~\cite{mcgill_calm_2013}.
This could explain why mathematical modeling has been extensively applied to microbial growth studies, creating a diversity a modeling framework.

@@

Models have to be tested with data.
Measuring growth = measuring biomass accumulation, over time, and get relevant information on the cell inner state.
We have a lot of data on this.

Population measurement is easy to implement, and allow to measure metabolites.
But small unsynchronized effects can be hidden since we mostly work with the mean.
Despite most of the knowledge we have on microorganism growth are from population measurements, like the RNA/DNA/etc ratios, the growth laws, etc.
Extensive work of Bremmer and Dennis.
Big discoveries of the last decades that rely on population measurements ? (cite 2 or 3)

Single-cell measurements lay on technologies like microscopy, fluorescence, FACS...
More interesting since we can use fluorescence to not just look at the cell but also measure interesting parameters (like gene expression) at the single-cell level.
Information on the localisation of DNA, ribosomes [Bakshi].
Variability in physiology, persistors, antibiotics resistance, etc [citations]

Both approaches can be performed either in batch or continuous conditions.
Batch conditions is the most straight forward in lab: you put sugar in a flask, they grow until nutrient is depleted.
Implemented in flash or petri-microscopy.
Resist to contamination.
It is close to natural conditions, and industrial conditions.
Has even been used to study long-term evolution of E. coli.
But the system is poorly control, mostly because the history of the cells play a huge role in the waking process.

Continuous culture consists into constantly providing nutrients to a culture, and maintaining it in a steady-state for a long time.
Implemented in bioreactor [citation] or microfluidic devices [mother machine citation].
Sensible to contaminations so hard to maintained (that's why industry ignore it so far).
Does not correspond to natural conditions but the system is fully controlled: perturbations can be applied and a lot of parameters can be monitored.
Possibility to let the cell long-enough in steady state to "forget" strain history.
Most suitable if one need to have full control on its system.

Finally, most of the work cited above are based on steady-state studies.
But there are also work in dynamic.
Levy showed that... in yeast.
Alon in Coli.
After decades working at steady-state, Bremmer and Dennis argued we should measure things during transitions.
de Jong / Gerosa showed that the gene expression machinery has its own dynamic that should be taken into account when measuring gene expression.
The evolutionary relevance of growth transitions has been emphasized in numerous others studies [citations lag phase, last generation before stationary, ...].

@@

@@

\section{Organisation of the dissertation}

(announcing the plan of the manuscript, which actually follow exactly the approach part, without the lenghty justifications)

>>>>

What makes mathematical modeling so useful in microbial growth studies?
Microbial physiology comes out from the interplay of thousands of chemical reactions that are not necessarily relevant in any given situation.
They usually occur on a short time scale as compared with the organism life span.
They nevertheless have been (and still are) selected by evolutionary processes that occur on long time scales.
These physical limitations strongly impede a full empirical study of growth processes, making sometimes hard to test the most simple verbal hypothesis.
Since they are designed to abstract away complexity, mathematical models are great tools to deal with such limitations.
The overwhelming number of variables and time scales can be dealt with by choosing the correct framework.
When working on a model, growth is abstracted into a world of clearly stated rules, where logical reasoning can be applied~\cite{servedio_not_2014}.
Predictions can be made, "unpacked" into our real world, and confronted with experimental testing.
In that sense, modeling is at the core of the scientific method~\cite{mcgill_calm_2013}.
This could explain why mathematical modeling has been extensively applied to microbial growth studies, creating a diversity a modeling framework.

@@

\textbf{Either to build models or test their predictions, data on microbial growth have to be acquired.}
Measuring growth = measuring biomass accumulation, over time, and get relevant information on the cell inner state.
We have a lot of data on this.

\textbf{Measuring population-wide parameters is convenient and provides robust data.}
Population measurement is easy to implement, and some things can only be measured at the population level (so far).
But small unsynchronized effects can be hidden since we mostly work with the mean.
Despite most of the knowledge we have on microorganism growth are from population measurements, like the RNA/DNA/etc ratios, the growth laws, etc.
Extensive work of Bremmer and Dennis.
Big discoveries of the last decades that rely on population measurements ? (cite 2 or 3)

\textbf{Single-cell measurements give access to data and behaviors that are hidden at the population level.}
Single-cell measurements lay on technologies like microscopy, fluorescence, FACS...
More interesting since we can use fluorescence to not just look at the cell but also measure interesting parameters (like gene expression) at the single-cell level.
Information on the localisation of DNA, ribosomes [Bakshi].
Variability in physiology, persistors, antibiotics resistance, etc [citations]

\textbf{Batch growing conditions are convenient and close to the natural conditions of bacteria, but they raise several problems.}
Both approaches can be performed either in batch or continuous conditions.
Batch conditions is the most straight forward in lab: you put sugar in a flask, they grow until nutrient is depleted.
Implemented in flash or petri-microscopy.
Resist to contamination.
It is close to natural conditions, and industrial conditions.
Has even been used to study long-term evolution of E. coli.
But the system is poorly control, mostly because the history of the cells play a huge role in the waking process.

\textbf{Continous cultures allow to precisely control the growing conditions.}
Continuous culture consists into constantly providing nutrients to a culture, and maintaining it in a steady-state for a long time.
Implemented in bioreactor [citation] or microfluidic devices [mother machine citation].
Sensible to contaminations so hard to maintained (that's why industry ignore it so far).
Does not correspond to natural conditions but the system is fully controlled: perturbations can be applied and a lot of parameters can be monitored.
Possibility to let the cell long-enough in steady state to "forget" strain history.
Most suitable if one need to have full control on its system.

\textbf{In all these practical conditions, one can choose to either measure cells at steady-state or in dynamic.}
Finally, most of the work cited above are based on steady-state studies.
But there are also work in dynamic.
Levy showed that... in yeast.
Alon in Coli.
After decades working at steady-state, Bremmer and Dennis argued we should measure things during transitions.
de Jong / Gerosa showed that the gene expression machinery has its own dynamic that should be taken into account when measuring gene expression.
The evolutionary relevance of growth transitions has been emphasized in numerous others studies [citations lag phase, last generation before stationary, ...].

@@

All of this is described in chapter 2.

@@

This, is described in chapter 3.
